Contracts for Contracts

### 2023-02-28 paper.tex
misc
title

%% Title information
\title[Short Title]{Contracts for Contracts}         %% [Short Title] is optional;
%\title[Short Title]{Contracts meet Contracts}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Adding Higher-Order Contracts for Smart Contracts}                     %% \subtitle is optional
%\subtitle{Expressive Assertion Monitoring System for Safer Smart Contracts}                     %% \subtitle is optional
\subtitle{Expressive Temporal Higher-Order Behavioral Contracts for Smart Contracts}                     %% \subtitle is optional
\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

informal description and examples of the language dubbed ``Contract Solidity''

@@

the core model of the language (TODO named?)
\todo{there must be some interesting points/trade-offs about the design}

>>>>

%% Title information
\title[Contracts for Contracts]{Contracts for Contracts}         %% [Short Title] is optional;
%\title[Short Title]{Contracts meet Contracts}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Adding Higher-Order Contracts for Smart Contracts}                     %% \subtitle is optional
%\subtitle{Expressive Assertion Monitoring System for Safer Smart Contracts}                     %% \subtitle is optional
\subtitle{Securing Smart Contracts with Higher-Order Temporal Behavioral Contracts}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

informal description and examples of the language dubbed \lang

@@

the core model of the language $\lambda_\lang$
\todo{there must be some interesting points/trade-offs about the design}
